---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# US26MIP

::: warn
> :warning: **This package is under development.**\
:::

<!-- badges: start -->
<!-- badges: end -->

The US26MIP is a version of USENSYS model developed for Model Intercomparison Project (MIP) with a goal of comparing capacity expansion models for the US power sector. The project used a common set of assumptions and data for 26-region model, assembled by PowerGenome and Princeton's Zero Lab. The US26MIP package provides the data, used in the project, and the model itself. It is organized as an R package and is intended to be used in conjunction with the `usensys` and `energyRt` packages.

## Installation

You can install the development version of US26MIP from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
# pak::pkg_install("usensys/usensys")
pak::pak("usensys/US26MIP")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(usensys)
library(US26MIP)
## basic example code
```

...
